Measuring the Price of Anarchy in Critical Care Unit Interactions

### 2014-12-21 Paper/paper.tex
Have re written the proof - needs to be checked

% New commands------------------------
\newcommand{\NH}{\text{NH}}
\newcommand{\RG}{\text{RG}}

@@

As \(\U_{\NH}\) increases from the lowest value (top left in Figure  \ref{fig:variation_of_UNH}) to the highest (bottom right in Figure \ref{fig:variation_of_UNH}) the value of \(U_{\NH}-t\) will change sign (from negative to positive).

%If $\lambda_{\NH}^{(l,l)}\leq \lambda_{\NH}^{(l,h)}$ and $\lambda_{\NH}^{(h,l)}\leq \lambda_{\NH}^{(h,h)}$, for given $K_{\NH}$: then as $K_{\RG}$ increases, the arrival rate at NH is non-increasing,
%Similarly, for given $K_{{\RG}}$, as $K_{\NH}$ increases the arrival rate at RG is non-decreasing.

%Using the above and the previous observation this implies:

%\begin{itemize}
    %\item The function $U_{\NH}=U_{\NH}(K_{\RG})$ is non-increasing;
    %\item The function $U_{\NH}=U_{\NH}(K_{\NH})$ is non-decreasing.
%\end{itemize}

%A graphical proof of the lemma is then shown in Figure \ref{proof}.

%\begin{figure}[!hbtp]
%\begin{center}
%\includegraphics[width=.7\textwidth]{./Images/proof.pdf}
%\end{center}
%\caption{Graphical proof of the fact that $f_{\NH}(K_{\RG})<f_{\NH}(K_{\RG}+1)$}\label{proof}
%\end{figure}

%Let $k^*=f_{NH}(K_{\RG})$ for a given $K_{\RG}$.
%As $K_{\RG}$ increases, the utilisation $U_{\NH}(k^*)$ will be non-increasing, but it will also be non-increasing for all $k<k^*$.
%As $K_{RG}$ increases $\left(U_{NH}(k^*)-t\right)^2$ decreases until $\left(U_{NH}(k^*)-t\right)^2$ is minimized and then increases, however $\left(U_{NH}(k^*+1)-t\right)^2$ will continue to decrease.
%Thus, $f_{\NH}(K_{\RG})\geq k^*$ as required.
\end{proof}

>>>>

% New commands------------------------
\newcommand{\NH}{\text{NH}}
\newcommand{\RG}{\text{RG}}
\DeclareMathOperator*{\argmin}{arg\!min}
\DeclareMathOperator*{\argmax}{arg\!max}

@@

As \(U_{\NH}\) increases from the lowest value (top left in Figure  \ref{fig:variation_of_UNH}) to the highest (bottom right in Figure \ref{fig:variation_of_UNH}) the value of \(U_{\NH}-t\) will change sign (from negative to positive).
Let \(f^+(K_{\RG})=\argmin_{\{0\leq k \leq C_{\NH}|U_{\NH}(k, K_{\RG})\geq t\}}(U_{\NH}(k, K_{\RG}))\) and \(f^-(K_{\RG})=\argmax_{\{0\leq k \leq C_{\NH}|U_{\NH}(k, K_{\RG})\leq t\}}(U_{\NH}(k, K_{\RG}))\).
So that \(f^{\pm}({K_{\RG}})\) is the value of \(K_{\NH}\) that gives the value of \(U_{\NH}(K_{\NH}, K_{\RG})\) that is closest to \(t\) such that:

\begin{equation}
U_{\NH}(f^-(K_{\RG}),K_{\RG})\leq t \leq U_{\NH}(f^+(K_{\RG}),K_{\RG})
\end{equation}

This immediately (from Figure \ref{fig:variation_of_UNH}) gives:

\begin{equation}
f^{\pm}(K_{\RG}) \leq f^{\pm}(K_{\RG} + 1)
\end{equation}

Let:

\begin{equation}
S(K_{\RG}) = \{f^{+}(K_{\RG})\}\cup\{f^{-}(K_{\RG})\}
\end{equation}

Thus, \(f(K_{\RG})\in S(K_{\RG})\).
Note that from (\ref{equ:UNH_as_a_function_of_KNH}) have \(\max S(K_{\RG})=f^{+}(K_{\RG})\) and \(\min S(K_{\RG})=f^{+}(K_{\RG})\).
In essence \(S(K_{\RG})\) corresponds to the set of two values of \(K_{\NH}\) that give a utilisation just below and just above \(t\).

There are two possibilities that will now be considered:

\begin{enumerate}
    \item \(S(K_{\RG})\ne S(K_{\RG})\)
    \item \(S(K_{\RG})= S(K_{\RG})\)
\end{enumerate}

If \(S(K_{\RG})\ne S(K_{\RG})\) this implies that \(f^{+}(K_{\RG})\leq f^{-}(K_{\RG})\) which gives:

\begin{equation}
    f(K_{\RG}) \leq f^{+}(K_{\RG}) \leq f^{-}(K_{\RG}+1) \leq f(K_{\RG}+1)
\end{equation}

which is the required result.

To finish the proof consider \(S(K_{\RG})= S(K_{\RG})\) and assume:

\begin{equation}
    f(K_{RG})=f^{+}(K_{\RG}) \text{ but } f(K_{RG}+1)=f^{-}(K_{\RG}+1)
\end{equation}

which contradicts the required result.

For simplicity of notation let:

\[a^{\pm}=(f^{\pm}(K_{\RG}), K{\RG})\text{ and }b^{\pm}=(f^{\pm}(K_{\RG}+1), K{\RG}+1)\]

Recalling equations (\ref{equ:UNH_as_a_function_of_KRG}-\ref{equ:UNH_as_a_function_of_KNH}) and Figure \ref{fig:variation_of_UNH} have:

\begin{align}
U_{\NH}(b^-)&\leq U_{\NH}(a^-)\\
U_{\NH}(b^+)&\leq U_{\NH}(a^+)
\end{align}

which implies:

\begin{equation}
U_{\NH}(b^-) +  U_{\NH}(b^+) \leq U_{\NH}(a^-) + U_{\NH}(a^-)
\label{equ:true_inequality_for_a_and_b}
\end{equation}

As \(f(K_{\RG})=f^{+}(K_{\RG})\) (this is the assumption made):

\begin{equation}
|U_{\NH}(a^+)-t|<|U_{\NH}(a^-)-t|
\end{equation}

this implies:

\begin{equation}
U_{\NH}(a^+)+U_{\NH}(a^-)<2t
\label{equ:contradiction_part_1}
\end{equation}

Similarly as \(f(K_{\RG}+1)=f^{-}(K_{\RG}+1)\) (this is the assumption made):

\begin{equation}
|U_{\NH}(b^+)-t|>|U_{\NH}(b^-)-t|
\end{equation}

this implies:

\begin{equation}
U_{\NH}(b^+)+U_{\NH}(b^-)>2t
\label{equ:contradiction_part_2}
\end{equation}

Combining (\ref{equ:contradiction_part_1}) and (\ref{equ:contradiction_part_2}) contradicts (\ref{equ:true_inequality_for_a_and_b}) implying that the original assumption was incorrect thus proving the required result.
\end{proof}
